\documentclass[10pt,a4paper]{article}
\usepackage[margin=3em]{geometry}
\usepackage{mdwlist}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xspace}

\newcommand{\Csharp}{%
  {\settoheight{\dimen0}{C}C\kern-.05em \resizebox{!}{\dimen0}{\raisebox{\depth}{\#}}}}

\newcommand{\latex}{\LaTeX\xspace}

% Configuration.
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]
{\begin{list}{}
  {\setlength{\leftmargin}{#1}} \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]
{\begin{list}{}
  {\setlength{\leftmargin}{-0.5#1}} \item[]
}
{\end{list}}
% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  #1 &
  #2 \\
\end{tabular*}}


\begin{document}


% Resume header.
\begin{center}
  \LARGE\textbf{Victor Hachard} \normalsize\emph{(June 6, 1999)} \\
  \href{mailto:victor.hachard@hotmail.fr}{victor.hachard@hotmail.fr}
  $\circ$
  0472 43 39 08 \\
  Rue Childéric 18, 7500 Tournai
  $\circ$
  Sriving license \\
  \href[pdfnewwindow=true]{http://www.github.com/VictorHachard}{github.com/VictorHachard}
  $\circ$
  \href[pdfnewwindow=true]{http://www.victorhachard.github.io}{victorhachard.github.io}
  $\circ$
  \href[pdfnewwindow=true]{http://www.victorhachard.fr}{victorhachard.fr}
\end{center}

% Skills section.
\vspace{-0.2em}
\begin{indentsection}{\parindent}
\begin{description*}
  \item[Languages:]
  French \emph{(mother tongue)}, English \emph{(full professional proficiency)}.
 \item[Langages :] Java, Python, PHP, SQL, C, \Csharp, HTML,
  CSS, JavaScript/jQuery, TypeScript, Shell, Bash.
  \item[Technologies :] Spring Boot, Angular, NSIS.
  \item[Systems:] Windows, Windows Server, Linux.
\end{description*}
\end{indentsection}


% Education section.
\subsection*{Education}
\begin{itemize}
  \parskip=0.1em
  \item
  \headerrow
    {\textbf{Bachelor's degree -- Computing and Systems} orientation Networks and Telecommunications}
    {\emph{2018 -- 2021}}
  \headerrow
    {Haute École en Hainaut, Mons, Belgium}
    {}
  \begin{itemize*}
    \setlength\itemsep{0.5em}
    \item[]
    Relevant assets learn: Routing and Switching, Development web-android, Object Oriented Design, Algorithms, Relational Database, Data Structures, Software Development.
    \item[]
    13-week internship at Technord where I created an installer with NSIS to simplify and accelerate the installation of software and a experimental web application with Angular in order to verify the viability of a new product.
  \end{itemize*}
  \item
  \headerrow
    {\textbf{Masters degree -- Computer Sciences}}
    {\emph{2017 -- 2018}}
  \headerrow
    {Umons, Mons, Belgium}
    {}
  \begin{itemize*}
    \item[]
    Relevant assets learn: computer operation, programming and algorithms, physics,
    mathematics.
   \item[]
   During my studies I learned a lot in programming, which confirmed my passion and therefore my studies.
  \end{itemize*}
  \item
  \headerrow
    {\textbf{Saint-Luc institute -- Photography/Art School}}
    {\emph{2015 -- 2018}}
  \headerrow
    {Tournai, Belgium}
    {\emph{}}
  \begin{itemize*}
    \item[]
    CESS/BAC, Certificate of photography technician, Certificate of basic management.
    \item[]
    During my studies I became more meticulous and more rigorous, it is the attention to detail that makes the photo magnificent.
    \item[]
    \rule{0pt}{2ex}\footnotesize My pictures @
    \href{http://www.victorhachard.fr}
    {victorhachard.fr}
  \end{itemize*}
\end{itemize}

 % Experience section.
\subsection*{Professional Experience}
\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{Student Job} -- meat counter}
    {\emph{2019 -- 2020}}
  \headerrow
    {{Carrefour EU, Froyennes, Belgium}}
    {\emph{}}
  \begin{itemize*}
    \item[]
    During this experience I was able to improve my communication with customer contacts as well as familiarize myself
    working in large companies.
  \end{itemize*}
  \item
  \headerrow
    {\textbf{Stagiaire éclairagiste}}
    {\emph{2012 -- 2015}}
  \headerrow
    {{Jet Sound, H\&D Technologie, Opéra Bastille, Belgium and France}}
    {\emph{}}
  \begin{itemize*}
    \item[]
    These internship were superb: I was a child making his dreams come true. The best time for me was to be at the lighting console
    of a show.
  \end{itemize*}
\end{itemize}

% Projects section.
\subsection*{Projects}
\begin{itemize}
  \parskip=0.1em
\iffalse
    \item
    \headerrow
      {\textbf{ \href[pdfnewwindow=true]{http://www.github.com/VictorHachard/user-application}
        {User web application}}}
      {\emph{2021}}
    \headerrow
      {\emph{Personal project in progress}}
      {\emph{}}
      \begin{itemize*}
        \item[]
        Application web - API REST.
        Apprentisage :  Java avancée, Spring Boot, Swagger, Angular (TypeScript).
      \end{itemize*}
\fi
    \item
    \headerrow
      {\textbf{\href[pdfnewwindow=true]{https://victorhachard.github.io/projects/naturopath-web-application}
        {Naturopath}} -- School work finish (TFE -- Bachelor's degree)}
      {\emph{2021}}
      \begin{itemize*}
        \item[]
        Creation of a web application - REST API: Naturopath which is a Wikipedia like. Users can view, add and edit pages. The administrators validate the content of the pages.
        Learn: Java avancé, Spring Boot, Swagger, Angular (TypeScript).
      \end{itemize*}
  \item
    \headerrow
        {\textbf{\href[pdfnewwindow=true]{https://victorhachard.github.io/projects/ypc}
      {YouTube Playlist Checker}} -- Personal project in progress}
        {\emph{2018 -- 2020}}
    \begin{itemize*}
      \item[]
      Creation of a web application : \href{http://www.ypc.yt}{ypc.yt} is a YouTube archiving site.
      Learn: PHP, SQL, database structure,
      creation of a web application/API from scratch, use of the YouTube API.
    \end{itemize*}
    \item
    \headerrow
      {\textbf{\href[pdfnewwindow=true]{https://victorhachard.github.io/projects/game-engine}
        {Game Engine}} -- Personal project in progress Soon\texttrademark}
      {\emph{2018}}
      \begin{itemize*}
        \item[]
        Creating a simple game engine. Learn : Java/JavaFX avancé,
        organisation/architecture d'un projet.
      \end{itemize*}
    \item
    \headerrow
      {\textbf{ \href[pdfnewwindow=true]{https://victorhachard.github.io/projects/boby-is-you}
        {Boby Is You}} -- School work finish}
      {\emph{2017}}
      \begin{itemize*}
        \item[]
        Remake of the game Baba Is You, by Hempuli.
        Learn: Java, JavaFX, files management, Apache Ant.
      \end{itemize*}
  \end{itemize}


% Interests/About section.
\begin{indentsection}{\parindent}
\begin{description*}
\item[Interests:]
  Computer/software architecture, computer hardware, teaching,
  manual, DIY.
\item[About me:]
  I’m committed to lifelong learning, punctual, reliable,
  good in oral communication, autodidact.
\end{description*}
\end{indentsection}


% Metalink.
\begin{center}
\footnotesize \latex source code @
\href{http://www.github.com/VictorHachard/resume}
{github.com/VictorHachard/resume} - fork @
\href{http://www.github.com/nixpulvis}
{github.com/nixpulvis}
\end{center}
\end{document}
