\begin{indentsection}{\parindent}
  \parskip=0.1em
\iffalse
    \item[]
    \headerrow
      {\textbf{ \href[pdfnewwindow=true]{http://www.github.com/VictorHachard/user-application}
        {User web application}}}
      {\emph{2021}}
    \headerrow
      {\emph{Personal project in progress}}
      {\emph{}}
      \begin{itemize*}
        \item[]
        Application web - API REST.
        Apprentisage :  Java avancée, Spring Boot, Swagger, Angular (TypeScript).
      \end{itemize*}
\fi
    \item[]
    \headerrow
      {\textbf{\href[pdfnewwindow=true]{https://victorhachard.github.io/projects/naturopath-web-application}
        {Naturopath}} -- School work finish (TFE -- Bachelor's degree)}
      {\emph{2021}}
      \begin{itemize*}
        \item[]
        Creation of a web application - REST API: Naturopath which is a Wikipedia like. Users can view, add and edit pages. The administrators validate the content of the pages.
        Learn: Java avancé, Spring Boot, Swagger, Angular (TypeScript).
      \end{itemize*}
    \item[]
    \headerrow
        {\textbf{\href[pdfnewwindow=true]{https://victorhachard.github.io/projects/ypc}
      {YouTube Playlist Checker}} -- Personal project in progress}
        {\emph{2018 -- 2020}}
    \begin{itemize*}
      \item[]
      Creation of a web application : \href{http://www.ypc.yt}{ypc.yt} is a YouTube archiving site.
      Learn: PHP, SQL, database structure,
      creation of a web application/API from scratch, use of the YouTube API.
    \end{itemize*}
    \item[]
    \headerrow
      {\textbf{\href[pdfnewwindow=true]{https://victorhachard.github.io/projects/game-engine}
        {Game Engine}} -- Personal project in progress}
      {\emph{2018}}
      \begin{itemize*}
        \item[]
        Creating a simple game engine. Learn: advanced Java/JavaFX,
        organization/architecture of a project.
      \end{itemize*}
    \item[]
    \headerrow
      {\textbf{ \href[pdfnewwindow=true]{https://victorhachard.github.io/projects/boby-is-you}
        {Boby Is You}} -- School work finish}
      {\emph{2017}}
      \begin{itemize*}
        \item[]
        Remake of the game Baba Is You, by Hempuli.
        Learn: Java, JavaFX, files management, Apache Ant.
      \end{itemize*}
  \end{indentsection}
